|

### 2023-04-07 paper.Rmd
small changes in 3.1

In diagnosing a model fit from residuals, we are generally interested in $H_0:$ *The regression model is correctly specified* against the broad alternative $H_a:$ *The regression model is misspecified*.

@@

One of the potential benefits of the visual test, based on the lineup protocol, is that it should be able to detect a range of departures from good residuals.

>>>>

In diagnosing a model fit from residuals, we are generally interested in *the regression model is correctly specified* ($H_0$) against the broad alternative  *the regression model is misspecified* ($H_a$).

@@

One of the potential benefits of the visual test, based on the lineup protocol, is that it works as an omnibus test,  able to detect a range of departures from good residuals.
